### 2024-03-25 thesis/sections/6.3-reference-resolution.tex
results

\subsection*{Results}
In the final setup, the agents are tasked with communicating objects with fewer infused human knowledge.
Table \ref{tab:results_dale_predictor_game} shows the results for the setup, in which the sender is pointed towards the target object with a human description based on the GRE algorithm.
Hereby, the 'CLEVR single' dataset acts as a baseline, to test if the agents are able to predict coordinates of objects at all.
In every configuration of the variables, the agents achieve a very high performance.
The worst average distance across the test dataset is 10 pixels, which still points onto an object.
Also the accuracy, which evaluates how many guesses of the receiver were pointing onto an object reflects this fact.
All configuration achieve an accuracy higher than 96,7\%.
% SD: Just occured to me: how do we measure accuracy if we are predicting numbers (numeric prediction)?
% DK: same as in the experiments with one model (done)
This aligns also with the results from the single neural models, where the average distance was similarly low.
In general, this shows that the agents are able to predict coordinates together.
However, the question arises if the message by the sender has actually an effect on the receivers' decision, or if the receiver learns to point towards the target coordinates on his own and the message is ignored.
Having a look at the transferred messages, it in fact shows that the receiver learns to point towards the target object on its own.
% SD: But how could it do so if the visual data is randomly distribution. It must rely on the message as that is the only source of information.
% DK: it does it in the same way as the single model above (TODO)
As in the experiment before, all communicated messages contain the same symbol independent of the input image.

>>>>

\subsection*{Results}
\begin{table}[ht]
    \centering
    \begin{tabular}{cc|cc|cc|cc}
        \toprule
                                      &         & \multicolumn{2}{c}{\textbf{Dale-2}} & \multicolumn{2}{c}{\textbf{Dale-5}} & \multicolumn{2}{c}{\textbf{CLEVR color}}                                                                                         \\  \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
        $n$                           & $|V|$   & \textbf{loss}                       & \textbf{Acc.}                       & \textbf{loss}                            & \textbf{Acc.}               & \textbf{loss}             & \textbf{Acc.}               \\\midrule
        \multicolumn{2}{c|}{baseline} & {34,49} & {34,3\%}                            & {38,13}                             & {30,31\%}                                & {42,72}                     & {18,28\%}                                               \\\midrule
        {1}                           & {2}     & \textcolor{purple}{34,91}           & \textcolor{purple}{34,81\%}         & \textcolor{purple}{40,61}                & {25,48\%}                   & {39,13}                   & {25\%}                      \\
        {1}                           & {10}    & \textcolor{purple}{35,31}           & {40,15\%}                           & \textcolor{purple}{38,73}                & {28,12\%}                   & \textcolor{purple}{44,19} & {20,53\%}                   \\
        {1}                           & {16}    & \textcolor{purple}{35,4}            & {42,93\%}                           & \textcolor{purple}{39,58}                & {26,17\%}                   & {39,64}                   & {24,18\%}                   \\
        {1}                           & {50}    & {32,64}                             & {42,01\%}                           & \textcolor{purple}{38,99}                & {28,52\%}                   & \textcolor{purple}{42,61} & {20,79\%}                   \\
        {1}                           & {100}   & \textcolor{purple}{36,73}           & \textcolor{purple}{31,21\%}         & \textcolor{purple}{40,25}                & {24,91\%}                   & \textcolor{purple}{41,5}  & {21,44\%}                   \\
        {2}                           & {2}     & \textcolor{purple}{33,76}           & {40,67\%}                           & {35,86}                                  & \textcolor{purple}{31,73\%} & \textcolor{purple}{41,79} & {22,14\%}                   \\
        {2}                           & {10}    & {31,37}                             & {43,27\%}                           & {37,23}                                  & \textcolor{purple}{30,34\%} & \textcolor{purple}{42,53} & \textcolor{purple}{19,75\%} \\
        {2}                           & {16}    & {31,19}                             & {46,27\%}                           & \textcolor{purple}{39,38}                & {28,21\%}                   & \textcolor{purple}{41,74} & {22,7\%}                    \\
        {2}                           & {50}    & \textcolor{purple}{33,66}           & {39,28\%}                           & \textcolor{purple}{39,62}                & {25,35\%}                   & \textcolor{purple}{45,63} & \textcolor{purple}{17,93\%} \\
        {2}                           & {100}   & \textcolor{purple}{35,1}            & \textcolor{purple}{34,81\%}         & \textcolor{purple}{39,86}                & {27,3\%}                    & \textcolor{purple}{45,45} & \textcolor{purple}{19,05\%} \\
        {3}                           & {2}     & {32,99}                             & {41,15\%}                           & {37,76}                                  & \textcolor{purple}{30,99\%} & \textcolor{purple}{46,45} & {20,92\%}                   \\
        {3}                           & {10}    & \textcolor{purple}{33,74}           & {38,89\%}                           & \textcolor{purple}{40,71}                & {26,48\%}                   & \textcolor{purple}{44,53} & \textcolor{purple}{19,01\%} \\
        {3}                           & {16}    & \textcolor{purple}{34,18}           & {38,98\%}                           & \textcolor{purple}{38,52}                & \textcolor{purple}{30,03\%} & \textcolor{purple}{41,22} & {21,53\%}                   \\
        {3}                           & {50}    & \textcolor{purple}{34,38}           & {38,93\%}                           & \textcolor{purple}{39,52}                & {26,74\%}                   & {38,4}                    & {24,87\%}                   \\
        {3}                           & {100}   & \textcolor{purple}{33,16}           & {40,19\%}                           & \textcolor{purple}{39,75}                & {27,78\%}                   & \textcolor{purple}{41,29} & {21,83\%}                   \\
        {4}                           & {2}     & \textcolor{purple}{33,48}           & {40,36\%}                           & \textcolor{purple}{38,28}                & \textcolor{purple}{30,9\%}  & \textcolor{purple}{42,53} & {22,4\%}                    \\
        {4}                           & {10}    & \textcolor{purple}{35,01}           & {39,97\%}                           & \textcolor{purple}{40,88}                & {26,39\%}                   & \textcolor{purple}{42,33} & {20,44\%}                   \\
        {4}                           & {16}    & \textcolor{purple}{35,59}           & \textcolor{purple}{35,59\%}         & \textcolor{purple}{37,91}                & \textcolor{purple}{31,86\%} & \textcolor{purple}{41,9}  & {20,27\%}                   \\
        {4}                           & {50}    & \textcolor{purple}{34,99}           & {36,68\%}                           & \textcolor{purple}{40,89}                & {23,26\%}                   & \textcolor{purple}{43,77} & \textcolor{purple}{18,36\%} \\
        {4}                           & {100}   & \textcolor{purple}{35,46}           & {37,46\%}                           & \textcolor{purple}{38,53}                & \textcolor{purple}{29,08\%} & {40,6}                    & {21,22\%}                   \\
        {6}                           & {2}     & \textcolor{purple}{34,97}           & {37,28\%}                           & \textcolor{purple}{39,52}                & \textcolor{purple}{29,69\%} & {40,53}                   & {24,7\%}                    \\
        {6}                           & {10}    & {32,39}                             & {43,53\%}                           & \textcolor{purple}{38,61}                & {28,26\%}                   & {40,84}                   & {21,74\%}                   \\
        {6}                           & {16}    & \textcolor{purple}{34,87}           & \textcolor{purple}{34,38\%}         & \textcolor{purple}{39,03}                & {26,82\%}                   & {40,34}                   & {23,31\%}                   \\
        {6}                           & {50}    & \textcolor{purple}{33,85}           & {37,07\%}                           & \textcolor{purple}{39,39}                & {27,17\%}                   & {40,8}                    & {22,09\%}                   \\
        {6}                           & {100}   & \textcolor{purple}{34,62}           & {40,02\%}                           & \textcolor{purple}{39,46}                & {25,48\%}                   & \textcolor{purple}{42,53} & \textcolor{purple}{18,4\%}  \\
        \bottomrule
    \end{tabular}
    \caption{TODO: caption}
    \label{TODO: label}
\end{table}

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|c|c|c}
        \toprule
                                      &           & \multicolumn{1}{c}{\textbf{Dale-2}} & \multicolumn{1}{c}{\textbf{Dale-5}} & \multicolumn{1}{c}{\textbf{CLEVR color}} \\  \cmidrule(lr){3-3}\cmidrule(lr){4-4}\cmidrule(lr){5-5}
        $n$                           & $|V|$     & \textbf{Probability mass}           & \textbf{Probability mass}           & \textbf{Probability mass}                \\\midrule
        \multicolumn{2}{c|}{baseline} & {62,16\%} & {49,61\%}                           & {41,68\%}                                                                      \\\midrule
        {1}                           & {2}       & {93,3\%}                            & {65,36\%}                           & \textcolor{purple}{39,22\%}              \\
        {1}                           & {10}      & {93,85\%}                           & \textcolor{purple}{46,97\%}         & \textcolor{purple}{40,1\%}               \\
        {1}                           & {16}      & {92,06\%}                           & {76,68\%}                           & \textcolor{purple}{36,43\%}              \\
        {1}                           & {50}      & {94\%}                              & {76,43\%}                           & \textcolor{purple}{39,97\%}              \\
        {1}                           & {100}     & {94,03\%}                           & \textcolor{purple}{54,14\%}         & \textcolor{purple}{40,27\%}              \\
        {2}                           & {2}       & {92,27\%}                           & \textcolor{purple}{52,15\%}         & \textcolor{purple}{33,64\%}              \\
        {2}                           & {10}      & {96,16\%}                           & {80,26\%}                           & \textcolor{purple}{36,53\%}              \\
        {2}                           & {16}      & {95,84\%}                           & {84,03\%}                           & \textcolor{purple}{39,65\%}              \\
        {2}                           & {50}      & {93,78\%}                           & \textcolor{purple}{52,24\%}         & \textcolor{purple}{39,56\%}              \\
        {2}                           & {100}     & {92,43\%}                           & \textcolor{purple}{53,23\%}         & \textcolor{purple}{37,68\%}              \\
        {3}                           & {2}       & {94,52\%}                           & \textcolor{purple}{51,97\%}         & \textcolor{purple}{37,09\%}              \\
        {3}                           & {10}      & {94,9\%}                            & \textcolor{purple}{53,47\%}         & \textcolor{purple}{38,24\%}              \\
        {3}                           & {16}      & {94,59\%}                           & {81,46\%}                           & {67,88\%}                                \\
        {3}                           & {50}      & {93,88\%}                           & {79,65\%}                           & \textcolor{purple}{40,36\%}              \\
        {3}                           & {100}     & {95,25\%}                           & \textcolor{purple}{48,52\%}         & \textcolor{purple}{42,55\%}              \\
        {4}                           & {2}       & {89,15\%}                           & \textcolor{purple}{51,98\%}         & \textcolor{purple}{39,68\%}              \\
        {4}                           & {10}      & {96,08\%}                           & \textcolor{purple}{48,03\%}         & {64,31\%}                                \\
        {4}                           & {16}      & {94,14\%}                           & \textcolor{purple}{49,81\%}         & \textcolor{purple}{40,84\%}              \\
        {4}                           & {50}      & {96,24\%}                           & \textcolor{purple}{48,79\%}         & \textcolor{purple}{43,61\%}              \\
        {4}                           & {100}     & {95,55\%}                           & \textcolor{purple}{49,65\%}         & \textcolor{purple}{42,85\%}              \\
        {6}                           & {2}       & \textcolor{purple}{59,68\%}         & \textcolor{purple}{53,57\%}         & \textcolor{purple}{38,43\%}              \\
        {6}                           & {10}      & \textcolor{purple}{63,46\%}         & {82,12\%}                           & \textcolor{purple}{40,11\%}              \\
        {6}                           & {16}      & {95,86\%}                           & \textcolor{purple}{50,71\%}         & \textcolor{purple}{40,61\%}              \\
        {6}                           & {50}      & {91,27\%}                           & \textcolor{purple}{52,55\%}         & \textcolor{purple}{40,21\%}              \\
        {6}                           & {100}     & \textcolor{purple}{60,27\%}         & \textcolor{purple}{46,92\%}         & \textcolor{purple}{41,98\%}              \\
        \bottomrule
    \end{tabular}
    \caption{TODO: caption}
    \label{TODO: label}
\end{table}

In the final setup, the agents are tasked with communicating objects with fewer infused human knowledge.
Table \ref{tab:results_dale_predictor_game} shows the results for the setup, in which the sender is pointed towards the target object with a human description based on the GRE algorithm.
Hereby, the 'CLEVR single' dataset acts as a baseline, to test if the agents are able to predict coordinates of objects at all.
In every configuration of the variables, the agents achieve a very high performance.
The worst average distance across the test dataset is 10 pixels, which still points onto an object.
Also the accuracy, which evaluates how many guesses of the receiver were pointing onto an object reflects this fact.
All configuration achieve an accuracy higher than 96,7\%.
% SD: Just occured to me: how do we measure accuracy if we are predicting numbers (numeric prediction)?
% DK: same as in the experiments with one model (done)
This aligns also with the results from the single neural models, where the average distance was similarly low.
In general, this shows that the agents are able to predict coordinates together.
However, the question arises if the message by the sender has actually an effect on the receivers' decision, or if the receiver learns to point towards the target coordinates on his own and the message is ignored.
Having a look at the transferred messages, it in fact shows that the receiver learns to point towards the target object on its own.
% SD: But how could it do so if the visual data is randomly distribution. It must rely on the message as that is the only source of information.
% DK: it does it in the same way as the single model above (TODO)
As in the experiment before, all communicated messages contain the same symbol independent of the input image.
